---
output: github_document
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# shoalsmaRinelab

<!-- badges: start -->
<!-- badges: end -->

The goal of the shoalsmaRinelab package is to provide users with custom palettes developed from landscapes and cuisine from the Shoals Marine Lab. 

## Installation

You can install the development version of shoalsmaRinelab from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("faithfrings/shoalsmaRinelab")
```

## Example

You can get a list of the possible palettes using `sml_palettes_available` function.

### Continuous example

```{r example}
library(shoalsmaRinelab)
library(ggplot2)

ggplot(faithful,
       aes(x = waiting,
           y = eruptions,
           color = eruptions))+
  geom_point()+
  scale_color_sml(palette = "sunset",
                  discrete = FALSE)+
  theme_bw()
```

### Discrete example

```{r}
ggplot(mpg, aes(x = class, fill = class)) + 
  geom_bar() + 
  scale_fill_sml(palette = "intertidal_critters",
                 discrete = TRUE) + 
  theme_bw()
```




